\chapter{Theoretical Motivation}

The Standard Model (SM) consists of 17 fundamental particles which together constitute every observed particle and most of the known forces.
It provides a remarkably precise fit to the majority of particle physics data, and predicted the $W$, $Z$, and Higgs bosons~\cite{wzmass1,higgs1,higgs2} decades before their discovery~\cite{ua1w,ua2w,ua1z,ua2z,atlashiggs,cmshiggs}.
For all its success, however, the Standard Model is an incomplete model of physics.

This is by design. The Standard Model is a verifiable and self-consistent description of the strong, weak, and electromagnetic interactions, but by definition it omits many phenomena.
Historically, the first such omission was gravitation; even today any attempts to incorporate gravity into particle theory are extremely speculative.
Recent observations have pointed to other glaring omissions:
%% neutrinos, massless in the Standard Model, clearly have mass;
the universe is filled with roughly 5 times more mysterious `dark matter' than visible matter;
and the visible matter shows a matter-antimatter asymmetry which can't be explained by SM processes.
Furthermore, the Standard Model appears `fine tuned'---very small shift in the constants of the model will completely change its behavior.

With the discovery of the Higgs boson, every major prediction of the Standard Model has been verified, leaving few hints as to the physical mechanism behind the omitted pieces.
The physics community now finds itself groping for another theory which can continue where the Standard Model left off. One promising candidate is Supersymmetry~\cite{susyprimer,srednicki,pdg2014}.
By postulating a new symmetry between bosons and ferminons, Supersymmetry (SUSY for short) predicts a \emph{superpartner} to each SM particle. Standard Model couplings to SUSY particles could produce dark matter, explain the observed matter-antimatter asymmetry in the universe, and hint at the structure of a framework to unify all of the forces.
They could also mitigate the fine-tuning issue within the standard model, provided that some SUSY particles are of comparable mass to their SM counterparts. This last feature is especially important from an experimental standpoint; superpartners with similar masses to the SM particles could be produced in accelerators.

The myriad of new particles predicted by SUSY are obvious targets for searches at the Large Hadron Collider (LHC). Over the last several years, both ATLAS and CMS have conducted many dozens of searches, none of which have discovered SUSY.
Since the exact properties of these hypothetical particles are unknown, the searches require a variety of approaches, and some versions of SUSY remain much more difficult to test.
This thesis documents a search for one particularly challenging scenario, where supersymmetric charm quarks ($\scharm$ quarks) decay to Standard Model charm quarks ($c$ quarks).
%% \footnote{The statement that searches have covered ``a large fraction of SUSY parameter space'' is heavily dependent on one's prior assumptions about SUSY. If one disregards the fine-tuning argument, there is less reason to assume SUSY should appear at energy scales accessible to the LHC.}
%% This thesis documents the search in one such patch of SUSY parameter space, specifically one in which supersymmetric particles decay to charm quarks.

This chapter is structured as follows:
\cref{sec:standard-model,sec:susy} give an overview of the Standard Model and Supersymmetry, in enough detail to motivate the search;
\cref{sec:susylimits} reviews the current state of SUSY searches;
and \cref{sec:pheno} describes the consequences of the Standard Model from the collider physics point of view. This chapter is not intended to be a comprehensive theoretical discussion of any of these subjects, as many excellent reverences already exist~\cite{pdg2014,peskin,srednicki,susyprimer}.

\input{tex/standard_model}
\input{tex/supersymmetry}
\input{tex/susylimits}
\input{tex/phenomenology}
