The reconstruction of jets and leptons is imperfect in any collider: a pion from a jet can resemble an electron; a $\tau$-lepton can resemble a jet; a $c$-jet can easily resemble a jet from QCD interactions in the underlying event.
Object definitions are thus a compromise between efficiency and fake rates.
Since events contain multiple objects, the optimal efficiencies and fake rates are very analysis dependent.
This section gives a detailed description of the object definitions in the $\sctoc$ search.

In general, objects are selected in three steps: first a ``preselected'' collection is formed for jets, electrons, and muons; next an overlap removal stage resolves ambiguity between objects, and finally ``signal'' objects are defined with more stringent quality requirements.

\subsection{Jets}
%% Hadronic QCD jets are orders of magnitude more common than leptons at the LHC.
%% They are also difficult to measure properly, since they consist of
Jets are formed from calorimeter clusters, which are clustered with the anti-$k_t$ algorithm~\cite{antikt} with a radius parameter of 0.4.
All jets are calibrated with a local cluster weighting~\cite{LCJets}.
In the case of simulated jets the same flavor labeling scheme as described in \cref{tag:sec:data-and-simulation} is applied. The preselected jets consist of all jets with with $\pt > 20\,\gev$. To remove electrons which have been reconstructed as jets, any jet with a preselected electron within $\Delta R < 0.2$ is discarded.

A number of quality requirements are applied to the preselected jets, as tabulated in \cref{tab:veryloosejet}. If a preselected jet fails any of these requirements, the entire event is discarded. These requirements rely on the following parameters~\cite{beam-backgrounds}:
\begin{description}
\item[$\emf$] The fraction of the jet energy deposited in the electromagnetic calorimeter.
\item[$\chf$] Charged jet fraction is defined as
  \begin{equation}
    \chf = \sum_{i \in \{\text{tracks}\}} \pt^{i} / \pt^{\text{jet}},
  \end{equation}
  where the sum is over all tracks associated to the jet.
\item[$\fmax$] Maximum fraction of calorimeter energy contained in one layer.
\item[$\nege$] Sum of negative energy in cells used by the jet.
\item[$\hecf$] Fraction of jet energy in the hadronic end cap.
\item[$\hecq$] Fraction of jet energy in the hadronic end cap which corresponds to cells with a $Q$-factor above 4000. The $Q$-factor is a measurement of pulse shape quality for a cell. It is defined as
\begin{equation}
  Q = \sum_{i \in \{\text{samples}\}} (m_i - s_i)^2
\end{equation}
where $m_i$ is the measured amplitude in sample $i$, and $s_i$ is the simulated amplitude for the same sample.
\item[$\larq$] Same as $\hecq$, but for the liquid argon calorimeter.
\item[$\qmean$] Average $Q$-factor for cells in the jet, weighted by energy squared.
\item[$\jvf$] Jet vertex fraction is the sum of the $\pt$ of tracks matched to the primary vertex divided by the $\pt$ sum of all tracks in a jet.
\end{description}

\begin{table}
  \begin{center}
    \input{tables/jetveryloose.tex}
    \caption[Jet \veryloose{} requirements]{Jet requirements to pass the \veryloose{} selection.}
    \label{tab:veryloosejet}
  \end{center}
\end{table}
\begin{table}
  \begin{center}
    \input{tables/jet.tex}
    \caption[Jet definitions]{Jet definitions.}
  \end{center}
\end{table}
\subsubsection{$c$-tagging Operating Points}
%% Charm tagging takes place before the final stage of calibration.
%% As such, the 
\subsection{Leptons}
\subsubsection{Electrons}
\begin{table}
  \begin{center}
  \input{tables/electron.tex}
  \caption[List of electron selection criteria]{Electron definitions.}
  \end{center}
\end{table}
\subsubsection{Muons}
\begin{table}
  \begin{center}
  \input{tables/muon.tex}
  \caption[List of muon selection criteria]{Muon definitions.}
  \end{center}
\end{table}
\subsection{Overlap Removal}
\subsection{Higher Vairables}
\begin{equation}
\meff = \sum_{i\leq n} (\pt^{\rm jet})_i + \met
\end{equation}
Most of this will be a table
\subsubsection{$\met$}

