\newcommand{\limitbandexplanation}{Observed limits are given by the solid red line. The dotted red lines indicate the maximum range of the observed exclusion when the signal cross section is varied by $\pm 1 \sigma$. Expected limits are given by the dotted blue line. The yellow band surrounding this line indicates the $1 \sigma$ confidence interval when including all sources of uncertainty listed in \cref{sec:systematics} except the signal cross section uncertainty.}


Following the validation checks described in \cref{sec:validation}, the signal regions were unblinded.
No excess over standard model expectations was observed. On the contrary, the the data show a deficit of roughly $1.5\sigma$ when both the background uncertainty and the statistical uncertainty in data are accounted for.
Overlays of data and expected standard model backgrounds are given in \cref{fig:unblinded-kinematics}.
The expected and observed counts in the three signal regions, when backgrounds are constrained only by control region data, are listed in \cref{tab:sr-yields}.

\begin{cfig}
  \graphic[0.49]{int/figures/stackplots/dans/signal_mct150/mass_cc.pdf}
  \graphic[0.49]{int/figures/stackplots/dans/signal_mct150/mass_ct.pdf}
  \caption[Unblinded $\mcc$ and $\mct$]{Unblinded distributions in $\mcc$ (left) and $\mct$ (right), with data and expected standard model backgrounds overlaid.
    Events in the $\mcc$ distribution are subjected to all cuts in the $\mctgt{150}$ region.
  }
  \label{fig:unblinded-kinematics}
\end{cfig}

\begin{table}
  \begin{center}
    \input{int/tables/generated/vrsr/vrcrsr/sr_fit/yieldtable}
    \caption[Background only fit extrapolated to signal region yields]{Results of the background-only fit for the signal regions. The uncertainty shown post-fit includes all systematic uncertainties listed in \cref{sec:systematics}.}
 %% {\bf The post-fit values will be updated upon unblinding to reflect the latest settings in the fit setup. Currently, the post-fit values shown are from an out-of-date setup.
    \label{tab:sr-yields}
  \end{center}
\end{table}


%% \section{Fit Results}

%% The fit is implemented by a collection of stacked software packages,
%% standard to the ATLAS SUSY group.
%% At the top level HistFitter~\cite{histfitter} is used.
%% This tool wrap the HistFactory~\cite{histfactory} package, which creates RooFit ``workspaces''.
%% These workspaces are fit, and $\cls$ is extracted, with HistFitter functions (which in turn call RooFit / RooStats).

%% Systematic variations are categorized as ``experimental'' and ``theoretical''.
%% The experimental systematics considered are described in \cref{sec:sys_experimental}.


\section{Limit Setting}

Lacking any excess in data over standard model backgrounds in the signal regions, we instead set 95\% $\cls$ exclusion limits in the scharm--neutralino mass plane, as shown in \cref{fig:plane_pretty_regions}. Upper limits for cross sections in the $\scharm$--$\neut$ plane are given in \cref{fig:exclusion_plane_ul}.

\subsection{Theory Systematic Combination}

Theoretical systematics for the backgrounds are derived as described in \cref{sec:sys_theorybkg}. When running the fit, theory systematics are not directly applied as yield variations in each region. Instead, the systematics are used to derive transfer factors from the region that best constrains each background to the other regions used in the fit, and the uncertainty for each region is calculated relative to the constraining region using these transfer factors. Uncertainties calculated in this way are discussed in \cref{sec:sys-theory}.
These uncertainties are further combined into overall theory systematics (those of the form ``overall down stat'' and ``overall up stat''). There are two important notes about the above procedure:
\begin{enumerate}
\item The theory systematics are calculated relative to the constraining region, meaning that the systematic variation {\em in} the constraining region is, by definition, zero.
\item Hypothetically, any region could be chosen as the constraining region for any background (e.g. we could quote uncertainties in every background relative to \crw). We choose to constrain the top backgrounds ($t + t \bar{t}$) using \crt, \wjets\ using \crw, and \zjets\ using \crz.
\end{enumerate}

Signal ISR and FSR uncertainties are described in \cref{sec:sys-theory}, and are added to the signal yields in all fits.
In accordance with SUSY group recommendations\footnote{See \url{https://twiki.cern.ch/twiki/bin/viewauth/AtlasProtected/SUSYLimitPlotting}},
signal cross-section uncertainties are shown only in the ``observed''
limits. An uncertainty band on the observed limits is calculated by
running three separate fits for each signal point: a nominal fit with
no cross section systematics applied, and a fit with ``up'' and ``down''
variations added to the expected signal yield.

\subsection{Exclusion Planes}
\label{sec:exclusions}

\begin{cfig}
  \graphic[0.8]{int/figures/limit_tree/full_exclusion/exclusion_inclusive.pdf}
\caption[Exclusion in the $m_{\scharm}$--$m_{\neut}$ plane]{
Exclusion in the $m_{\scharm}$--$m_{\neut}$ plane, using the three $\mct$ fit configurations and the boosted C1 and C2 configurations. The monojet exclusion is shown for comparison, as is flavor-blind 2--6 jet exclusion~\cite{atlas-inclusive}. \limitbandexplanation}
\label{fig:plane_pretty_regions}
\end{cfig}

\begin{cfig}
\graphic[0.8]{int/figures/limit_tree/full_exclusion/exclusion_best.pdf}
\caption[Best signal regions in the $m_{\scharm}$--$m_{\neut}$ plane]{%
Expected and observed exclusion in the $m_{\scharm}$--$m_{\neut}$ plane.
Points with $\cls < 0.05$ are considered excluded.
The three signal regions, with $\mct = \{150, 200, 250\}\text{ GeV}$ are combined with the two $\tilde{t} \to c \neut$ regions (C1 and C2), by taking the region which produces the minimum $\cls$ for each point.}
\label{fig:plane_best_regions}
\end{cfig}

The expected exclusion (based on the fit setup described in
\cref{sec:regions-and-fitting}) is shown in
\cref{fig:plane_best_regions}. The three $\mct$ fit
configurations---those described in this thesis---are considered, each
consisting of the three control regions and one of the three signal
regions defined by the $\mct$ requirement, for a total of four regions
per fit.
In all cases the uncertainties described in \cref{sec:systematics} are accounted for with additional fit parameters.
In addition, we consider two \emph{boosted} signal regions (C1 and C2) from the $\tilde{t} \to c\neut$~\cite{stopCharmATLAS} analysis.
While the $\mct$ signal regions are optimized for high $\Delta m \equiv m_{\scharm} - m_{\neut}$ signal points with two resolvable $c$-jets, these regions loose sensitivity for low $\Delta m$ values, as shown in
\cref{fig:plane_regions_expected}.
The boosted regions, by contrast, are optimized for ISR boosted $c$-jets, and are sensitive to signal points with low $\Delta m$.
Exclusions from individual fit configurations are given in \cref{fig:exclusion_plane_ul}, along with 95\% $\cls$ $\scharm$ cross-section upper limits.

The five fit configurations are merged by taking the ``best'' configuration---that which is expected to exclude the signal with the highest confidence---for each signal point. Contours for the expected and observed exclusion are drawn by interpolating between signal points. Simple linear interpolation of $\cls$, however,  is known to introduce a bias because $\cls$ is relatively non-linear as a function of both $\scharm$ and $\neut$ mass. Following the precedent from previous SUSY searches~\cite{susy-limit-setting}, the $\cls$ values at each signal point are transformed to Gaussian significance $Z$ using the Gaussian inverse cumulative distribution function. Linear interpolation is then used to define $Z(m_{\scharm}, m_{\neut})$ for all points in the plane and draw contours where $Z(m_{\scharm}, m_{\neut}) = Z_{95 \% \text{ CL}} \approx 1.645$.

 %% The interpolation in the \scharm--\neut plane is discussed further in \cref{sec:cls-interpolation}, while
%% Cross-checks of indivial signal points are discussed in \cref{sec:fit-signal-points}.


\clearpage

\subsection{Model Independent Upper Limits}
\label{sec:model-independent-ul}

Model independent upper limits on non--Standard Model physics are
derived using a ``discovery'' fit, in which we assume the hypothetical
process only contributes to the signal region yield and leaves the
control regions unaffected. One discovery fit is run for each signal
region. This fit is considerably simpler than the exclusion fit;
whereas the exclusion fit accounts for all systematic variations and
fits the control and signal regions simultaneously, each discovery fit
considers a single signal region with a single combined background
estimate. Expected standard model background yields, observed yields,
and a single overall background uncertainty are taken directly from
\cref{tab:sr-yields}. Fit results are converted to upper limits by
solving for $\cls(\mu) = 0.05$, where $\mu$ is the signal
strength. The $\cls(\mu)$ values themselves are calculated with both
asymptotic formulae~\cite{asymptotics} and by running with 3000
pseudo-experiments to derive test statistic distributions.  The result
is a 95\% $\cls$ upper limit on the visible cross section, as summarized
in \cref{tab:model-ind-lim}.

\begin{table}
\centering
\subfigure[asymptotic limits]{
\input{int/tables/model_independent_upper_limits/UpperLimitTable_asimov.tex}
\label{tab:miul-asymtotic}
}
\subfigure[limit with 3000 toys]{
\input{int/tables/model_independent_upper_limits/UpperLimitTable_nToys3000.tex}
\label{tab:miul-toys}
}
\caption[Breakdown of model independent upper limits]{
Model independent upper limits calculated using asymtotic approximations~\subref{tab:miul-asymtotic} and with 3000 pseudo-experiments~\subref{tab:miul-toys}. Left to right: 95\% CL upper limits on the visible cross section
($\langle\epsilon\sigma\rangle_{\rm obs}^{95}$) and on the number of
signal events ($S_{\rm obs}^{95}$ ).  The third column
($S_{\rm exp}^{95}$) shows the 95\% CL upper limit on the number of
signal events, given the expected number (and $\pm 1\sigma$
excursions on the expectation) of background events.
The last two columns
indicate the $CL_B$ value, i.e. the confidence level observed for
the background-only hypothesis, and the discovery $p$-value ($p(s = 0)$).}
\label{tab:model-ind-lim}
\end{table}



%% \cite{histfitter}.
